\bfseries LaTeX Book Sample

### 2021-12-04 book-en/book-en.tex
Update

%----- usepackage for tempalate -----
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs,bm}
%\usepackage[notcite,notref]{showkeys}
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=1.7cm,bottom=1.8cm,includehead,includefoot}
%\geometry{left=1in,right=1in,top=1in,bottom=1in}
%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
\usepackage{url,hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black} % 去掉目录红框
\usepackage[english]{babel}
\usepackage{imakeidx}
\usepackage{color,xcolor}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{tabularx,array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{fancybox}
\usepackage{makecell}
\usepackage{xstring}
%\usepackage[english]{babel}
\usepackage{listings}
\usepackage{titletoc}
\usepackage{titlesec}
\usepackage{mathtools}
\usepackage{float}
\usepackage{bookmark}
\usepackage[numbers]{natbib}

%\usepackage{indentfirst}
\usepackage[perpage,symbol]{footmisc}   % footnote control

@@

\title{THE BOOK \\[8pt] \LaTeX ~TEMPLATES}
\author{John Smith}
\date{\today}

@@

%\maketitle

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage} % Suppresses headers and footers on the title page

    \pdfbookmark[0]{Cover}{cover} % book cover

	\centering % Centre everything on the title page

	\scshape % Use small caps for all text on the title page

	\vspace*{2\baselineskip} % White space at the top of the page

	%------------------------------------------------
	%	Title
	%------------------------------------------------

	\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt} % Thick horizontal rule
	\rule{\textwidth}{0.4pt} % Thin horizontal rule

	\vspace{0.75\baselineskip} % Whitespace above the title

    \makeatletter

	{\LARGE\bfseries \@title \\} % Title

	\vspace{0.75\baselineskip} % Whitespace below the title

	\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt} % Thin horizontal rule
	\rule{\textwidth}{1.6pt} % Thick horizontal rule

	\vspace{2\baselineskip} % Whitespace after the title block

	%------------------------------------------------
	%	Subtitle
	%------------------------------------------------

	% A Number of Fascinating and Life-changing Templates Presented in a Clear and Concise Way

	\vspace*{3\baselineskip} % Whitespace under the subtitle

	%------------------------------------------------
	%	Editor(s)
	%------------------------------------------------

	Edited By

	\vspace{0.5\baselineskip} % Whitespace before the editors

	{\scshape\Large \@author \\} % Editor list

	\vspace{0.5\baselineskip} % Whitespace below the editor list

	\textit{The University Name} % Editor affiliation

	\vfill % Whitespace between editor names and publisher logo

    \makeatletter

	%------------------------------------------------
	%	Publisher
	%------------------------------------------------

	\plogo % Publisher logo

	\vspace{0.3\baselineskip} % Whitespace under the publisher logo

	2021 % Publication year

	{\large publisher} % Publisher

\end{titlepage}

>>>>

%----- Packages for template -----
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{mathrsfs,bm}
%\usepackage[notcite,notref]{showkeys}
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=1.7cm,bottom=1.8cm,includehead,includefoot}
%\geometry{left=1in,right=1in,top=1in,bottom=1in}
%\geometry{left=2.5cm,right=2.1cm,top=1.7cm,bottom=2cm,includehead,includefoot}
%\geometry{b5paper,text={125mm,195mm},centering,left=1in,right=1in,top=1in,bottom=1in}
\usepackage{url,hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black}
\usepackage[english]{babel}
\usepackage{imakeidx}
\usepackage{color,xcolor}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{tabularx,array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{fancybox}
\usepackage{makecell}
\usepackage{xstring}
%\usepackage[english]{babel}
\usepackage{listings}
\usepackage{titletoc}
\usepackage{titlesec}
\usepackage{mathtools}
\usepackage{float}
\usepackage{bookmark}
\usepackage[numbers]{natbib}

%\usepackage{indentfirst}
\usepackage[perpage,symbol]{footmisc}   % footnote setting

@@

\title{\bfseries LaTeX Book Sample}
\author{Edited by John Smith}
\date{\today}

@@

\maketitle
